%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Conferences}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {\textbf{CVPR}, 2024. Poster presentation. Seattle, WA, USA.}

    \cvpub {\textbf{ECML PKDD}, 2023. Workshop chair \href{https://sites.google.com/view/dlspa-ecmlpkdd2023/}{\textit{``Deep Learning for Sustainable Precision Agriculture"}}. Turin, Italy.}

    \cvpub {\textbf{ECML PKDD}, 2023. Poster presentation \textit{``Domain Generalization for Crop Segmentation with Knowledge Distillation"}. Turin, Italy.}
    
    \cvpub {\textbf{ECML PKDD}, 2022. Poster presentation \textit{``Waypoint Generation in Row-based Crops with Deep Learning and Contrastive Clustering"}. Grenoble, France.}

    \cvpub {\textbf{SAI Computing Conference}, 2022. Oral presentation \textit{``Ultra-Low-Power Range Error Mitigation for Ultra-Wideband Precise Localization"}. London, UK.}

    \cvpub {\textbf{IRIM Conference}, 2021. Poster presentation \textit{``Local Planners with Deep Reinforcement Learning for Indoor Autonomous Navigation"}. Rome, Italy.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Other Events}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {\textbf{PhD Poster Day}, 2024.\ Poster presentation \textit{``Efficient and Robust Deep Learning Models for Service Robotics"}. Politecnico di Torino, Turin, Italy.}

    \cvpub {\textbf{PhD Poster Day}, 2023.\ Poster presentation \textit{``Knowledge Distillation for Efficient and Robust Deep Learning Models"}. Politecnico di Torino, Turin, Italy.}
    
    \cvpub {\textbf{PhD Poster Day}, 2022.\ Poster presentation \textit{``Efficient Deep Learning models for Robot perception, control, and decision-making"}. Politecnico di Torino, Turin, Italy.}

    \cvpub {\textbf{Data, AI, and Robotics @PoliTo}, 2021.\ Poster presentation \textit{``AI@PIC4SeR"}. Turin, Italy.}
\end{cvpubs}