%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}

    \cvpub{Cerrato, S., Mazzia, V., Salvetti, F., Martini, M., \textbf{Angarano, S.}, Navone, A., \& Chiaberge, M. (2024). A Deep Learning-driven Algorithmic Pipeline for Autonomous Navigation in Row-based Crops. IEEE Access.}
    
    \cvpub{\textbf{Angarano, S.}, Martini, M., Salvetti, F., Mazzia, V., \& Chiaberge, M. (2024). Back-to-Bones: Rediscovering the Role of Backbones in Domain Generalization. Pattern Recognition, 110762.}

    \cvpub{\textbf{Angarano, S.}, Martini, M., Navone, A., \& Chiaberge, M. (2024). Domain Generalization for Crop Segmentation with Standardized Ensemble Knowledge Distillation. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (pp. 5450-5459).}
    
    \cvpub{Navone, A., Martini, M., Ostuni, A., \textbf{Angarano, S.}, \& Chiaberge, M. (2023). Autonomous Navigation in Rows of Trees and High Crops with Deep Semantic Segmentation. In 2023 European Conference on Mobile Robots (ECMR) (pp. 1-6). IEEE.}
    
    \cvpub{Navone, A., Martini, M., \textbf{Angarano, S.}, \& Chiaberge, M. (2023). Online Learning of Wheel Odometry Correction for Mobile Robots with Attention-based Neural Network. In 2023 IEEE 19th International Conference on Automation Science and Engineering (CASE). IEEE.}
    
    \cvpub{\textbf{Angarano, S.}, Salvetti, F., Martini, M., \& Chiaberge, M. (2023). Generative Adversarial Super-resolution at the Edge with Knowledge Distillation. Engineering Applications of Artificial Intelligence, 123, 106407.}

    \cvpub{Marchionna, L., Pugliese, G., Martini, M., \textbf{Angarano, S.}, Salvetti, F., \& Chiaberge, M. (2023). Deep Instance Segmentation and Visual Servoing to Play Jenga with a Cost-Effective Robotic System. Sensors, 23(2), 752.}

    \cvpub{Salvetti, F., \textbf{Angarano, S.}, Martini, M., Cerrato, S., \& Chiaberge, M. (2022). Waypoint Generation in Row-based Crops with Deep Learning and Contrastive Clustering. In Machine Learning and Knowledge Discovery in Databases: European Conference, ECML PKDD 2022, Grenoble, France, September 19–23, 2022, Proceedings. Springer International Publishing.}
    
    \cvpub{Mazzia, V., \textbf{Angarano, S.}, Salvetti, F., Angelini, F., \& Chiaberge, M. (2022). Action Transformer: A Self-attention Model for Short-time Pose-based Human Action Recognition. Pattern Recognition, 124, 108487.}

    \cvpub{Martini, M., Cerrato, S., Salvetti, F., \textbf{Angarano, S.}, \& Chiaberge, M. (2022). Position-Agnostic Autonomous Navigation in Vineyards with Deep Reinforcement Learning. In 2022 IEEE 18th International Conference on Automation Science and Engineering (CASE) (pp. 477-484). IEEE.}
    
    \cvpub{\textbf{Angarano, S.}, Salvetti, F., Mazzia, V., Fantin, G., Gandini, D., \& Chiaberge, M. (2022). Ultra-Low-Power Range Error Mitigation for Ultra-Wideband Precise Localization. In Science and Information Conference (pp. 814-824). Springer, Cham.}

    \cvpub{Martini, M., Mazzia, V., \textbf{Angarano, S.}, Gandini, D., \&
    Chiaberge, M. (2021). Local Planners with Deep Reinforcement Learning for Indoor Autonomous Navigation. In 2021 I-RIM Conference (pp. 157-160). I-RIM.}
    
    \cvpub{\textbf{Angarano, S.}, Mazzia, V., Salvetti, F., Fantin, G., \& Chiaberge, M. (2021). Robust Ultra-wideband Range Error Mitigation with Deep Learning at the Edge. Engineering Applications of Artificial Intelligence, 102, 104278.}
    
\end{cvpubs}

%---------------------------------------------------------
\cvsubsection{Accepted}
%---------------------------------------------------------
\begin{cvpubs}

    \cvpub{Navone, A., Martini, M., \textbf{Angarano, S.}, \& Chiaberge, M. (2023). Lavender Autonomous Navigation with Semantic Segmentation at the Edge. Accepted at ECML PKDD 2023 Workshop "\href{https://sites.google.com/view/dlspa-ecmlpkdd2023/}{Deep Learning for Sustainable Precision Agriculture}" (Turin, Italy).}
    
\end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{Under Review}
% %---------------------------------------------------------

\begin{cvpubs}

    \cvpub{Navone, A., Martini, M., Ambrosio, M., Ostuni, A., \textbf{Angarano, S.}, \& Chiaberge, M. (2024). GPS-free Autonomous Navigation in Cluttered Tree Rows with Deep Semantic Segmentation. arXiv preprint arXiv:2404.05338.}
    
\end{cvpubs}

